Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Reformat whole kernel bounds for move into {sec:V is a contraction}

Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. We'll use these bounds in Section~\ref{sec:V is a contraction}. \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else? If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
\subsubsection{Bounds near the origin}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.

Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.

Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$, which means that
\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.

Putting these results together, we see that for any $\sigma > \tau$, we can ensure that
\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
by keeping $a$ and $a'$ close enough to $\zeta = 0$.
\subsubsection{Bounds away from the origin}
We can also bound the kernel $\kerwhole$ when $a$ is kept away from $\zeta = 0$. Suppose $\hardpart$ satisfies Condition~\eqref{cond:diag-basic} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then
\begin{align*}
|\kerwhole(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
&\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
%&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$. Since $|\zeta(a)-\zeta(a')|^\epsilon$ has power-law growth, we can bound it with any exponential. In other words, for any $\lambda > \lambda_\Delta$,
\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$. It follows that
\[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$.
%\color{Tomato}
%\begin{align*}
 %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
  %  &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
   % &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
%\end{align*}
%Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

%\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%We deduce that

%\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.

%\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely

%\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}

%\begin{verify}
 %   \begin{align*}
  %      \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
   %     &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
    %    &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    %\end{align*}
%\end{verify}
%\color{black}

%notice that $\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon$ is bounded by a constant which depends on $|\zeta(a')|$ (and of course on $\delta$ and $\epsilon$)

\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}

@@

\textcolor{orange}{[Read through and revise]} In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $\textcolor{orange}{\delta}$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$. Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.

@@

Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \textcolor{orange}{\delta}$ for these points:
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt. \]

We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$. To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately. At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
\begin{align*}
\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\lambda)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
& = e^{-\frac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
\end{align*}
At the end of the path, we instead use a worst-case estimate on $t^{1-\rho}$:
\begin{align*}
\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt \\
& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}} \right] \\
& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}.
\end{align*}

We now know that by setting $\Lambda > \lambda + \textcolor{orange}{\delta}^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. \textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$. To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above. To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of a fixed point \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

@@

 \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

@@

The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$ and

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.}  
\]

We should be able to deduce from this that
\begin{align*}
f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
\end{align*}
when we restrict to $\domain_\text{near}$.
\color{black}
\end{proof}

>>>>

Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
%%We'll use these bounds in Section~\ref{sec:V is a contraction}. \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else? If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
\begin{prop}\label{prop:whole-ker-near-bound}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
by keeping $a$ and $a'$ close enough to $\zeta = 0$.
\end{prop}
\begin{proof}
Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.

Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$, which means that
\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Combining this conclusion with the previous one, we get the desired result.
\end{proof}
Another bound, which works when the first argumetn of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
\begin{prop}\label{prop:whole-ker-far-bound}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Choose a subset $\domain_\text{far} \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
\[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
over all $a \in \domain_\text{far}$ and $a' \in \domain$.
\end{prop}
\begin{proof}
Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\domain_\text{far}$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that
\begin{align*}
|\kerwhole(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
&\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since
\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \]
grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$. It follows that
\[ |\kerwhole(a,a')| \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a \in \domain_\text{far}$ and $a' \in \domain$. This simplifies to the desired result.
\end{proof}.
\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}

@@

In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $\delta$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$. Complementarily, let $\far$ be the part of $\domain$ where $\delta \le |\zeta|$.

@@

Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]

We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$. To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately. At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
\begin{align*}
\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\lambda)\delta} \int_0^{1/5} t^{\rho-1}\;dt \\
& = e^{-\frac{4}{5}(\Lambda - \lambda)\delta}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
\end{align*}
At the end of the path, we instead use a worst-case estimate on $t^{1-\rho}$:
\begin{align*}
\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt \\
& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\delta} \right] \\
& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}.
\end{align*}

We now know that by setting $\Lambda > \lambda + \delta^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. \textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$. To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above. To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of a fixed point \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

@@

 %\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

@@

The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
\begin{verify}
By definition of limit, as $\zeta(a)\to\alpha$ we should get
\[
\left\vert\frac{1}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...}-\frac{1}{p'(\alpha)}\right\vert\leq \varepsilon
\]
\end{verify}

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.} |\zeta(a)-\alpha| + O(|\zeta(a)-\alpha|^2)
\]

Therefore, we deduce from this that
\begin{align*}
f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
\end{align*}
when we restrict to $\domain_\text{near}$.
\color{black}
\end{proof}
